%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Darwin Recruitment - Senior Application Support Engineer (L2/L3) - Stockholm}, pdfauthor={Manisha Padhi}, pdfsubject={Senior Application Support Engineer (L2/L3) - Stockholm}, pdfkeywords={Senior Application Support Engineer | L2/L3 Production Support | Java \& Spring Boot}}

\name{Manisha}{Padhi}

\position{Senior Application Support Engineer | L2/L3 Production Support | Java \& Spring Boot}

\address{Stockholm, Sweden | Female | EU long-term residence permit | No sponsorship required}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Professional Summary}
\vspace{-0.5ex}
\noindent\descriptionstyle{Senior software and application support professional with 8+ years of enterprise IT experience, including 3+ years focused on Java/Spring Boot backend systems, production support and operational reliability.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Experienced supporting business-critical applications through incident analysis, root-cause investigation, release readiness, monitoring, stakeholder communication and cross-functional coordination.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Strong fit for L2/L3 application support in telecom or high-availability environments, with practical experience in Java services, REST APIs, SQL databases, CI/CD, observability and production troubleshooting.}\par

\cvsection{Selected Achievements and Highlights}
\begin{cvitems}
  \item {Supports critical production systems by analyzing incidents, coordinating fixes, validating releases and communicating status with technical and non-technical stakeholders.}
  \item {Applies Java, Spring Boot, REST API, SQL/PostgreSQL, Redis, Docker, Kubernetes, CI/CD and observability experience to diagnose and stabilize application behaviour.}
  \item {Uses Grafana, Prometheus, NewRelic, logs and metrics to investigate production issues, identify patterns and improve operational reliability.}
  \item {8+ years of enterprise IT experience, including 3+ years focused on Java/Spring Boot backend development for production systems.}
  \item {Recognized career progression: promoted from Associate Trainee to Associate Consultant within 1 year.}
  \item {CMMI certified within 2 years and ranked top 3 in a Java certification course, supporting a quality-focused engineering profile.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Application support}{L2/L3 production support, incident analysis, root-cause investigation, release validation, operational handover, stakeholder communication}
  \cvskill{Java stack}{Java 17/21, Spring Boot, Spring WebFlux, REST APIs, Maven, JUnit, Mockito, integration testing, clean code practices}
  \cvskill{Runtime and data}{JBoss application server context, PostgreSQL, SQL, MySQL concepts, Redis, JSON, XML, data validation, query troubleshooting}
  \cvskill{ITSM operations}{Incident Management, Problem Management, Change Management, ITIL process alignment, ServiceNow-style ticket workflows}
  \cvskill{Observability and automation}{Grafana, Prometheus, NewRelic, logging, metrics, alerting, CI/CD, Docker, Kubernetes, GitHub Actions, Linux}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Support business-critical Java 17 backend services and REST APIs in production, taking ownership of incidents from investigation through fix validation and release follow-up.}
  \item {Troubleshoot production behaviour using logs, metrics, Grafana, Prometheus and NewRelic, identifying root causes across application logic, integrations and data handling.}
  \item {Work with product owners, QA, DevOps and engineers to clarify incidents, prioritize fixes, coordinate releases and communicate operational status.}
  \item {Maintain Spring Boot and Spring WebFlux services backed by PostgreSQL, SQL, Redis, JSON and XML, with focus on reliable data handling and service behaviour.}
  \item {Improve supportability through automated tests, integration checks, API validation, documentation and repeatable handover workflows.}
  \item {Use Docker, Kubernetes, Git, GitHub Actions, Maven and CI/CD practices to support stable deployment, release readiness and operational continuity.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
\end{cvskills}

\end{document}
