%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - Developer for TRATON R\&D IoT Gateway}, pdfauthor={Manisha Padhi}, pdfsubject={Developer for TRATON R\&D IoT Gateway}, pdfkeywords={Backend Developer | IoT Gateway | Cloud Connectivity | DevSecOps}}

\name{Manisha}{Padhi}

\position{Backend Developer | IoT Gateway | Cloud Connectivity | DevSecOps}

\address{Lgh 1301, Skoldvagen 7, Stockholm, 15151, Sweden}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Target Role}
\begin{cvskills}
  \cvskill{Company and role}{Scania - Developer for TRATON R\&D IoT Gateway}
  \cvskill{Location}{Sodertalje / Stockholm region, Sweden}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\cvsection{Professional Summary}
\begin{cvskills}
  \cvskill{Summary}{Senior backend developer with 8+ years of experience and 3+ years focused on Java, Spring Boot, REST APIs, microservices, databases, production systems and agile delivery.}
  \cvskill{Summary}{Strong match for TRATON R\&D IoT Gateway through backend service development, cloud and container exposure, secure integrations, CI/CD, monitoring, production support and interest in vehicle connectivity.}
  \cvskill{Summary}{Can contribute to robust communication platforms by building APIs, internal tools, event-ready services, test automation and operational improvements with a DevSecOps mindset.}
\end{cvskills}

\cvsection{Target Role Fit}
\begin{cvitems}
  \item {Build, test, deploy and maintain backend services and internal tools with end-to-end ownership and production accountability.}
  \item {Experience with REST APIs, microservices, Docker, Kubernetes, CI/CD, Grafana, databases and clean maintainable backend code.}
  \item {Project exposure to AWS CDK, Docker and CI/CD through Smart Trader cloud data platform; strong interest in AWS/cloud-native development.}
  \item {Relevant secure communication mindset through JWT, OAuth2, role-based access control, secure interfaces and API validation.}
  \item {Ready to transfer Java backend experience into C\#/.NET ecosystems while contributing immediately to API design, testing, monitoring and DevSecOps practices.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Backend}{Java 17/21, Spring Boot, Spring WebFlux, REST APIs, microservices, internal tools, maintainable code, clean architecture awareness}
  \cvskill{Cloud and DevSecOps}{Docker, Kubernetes, GitHub Actions, CI/CD, AWS CDK exposure, Maven, Linux, infrastructure-as-code interest}
  \cvskill{Connectivity fit}{IoT interest, vehicle connectivity interest, secure communication, API integration, message routing, event-driven architecture awareness}
  \cvskill{Security}{JWT, OAuth2, role-based access control, secure APIs, certificate/PKI awareness, DevSecOps mindset}
  \cvskill{Operations}{Grafana, Prometheus, NewRelic, logging, metrics, alerting, troubleshooting, SQL, PostgreSQL, Redis}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Develop and maintain Java 17 backend services and REST APIs for business-critical production systems with end-to-end ownership.}
  \item {Build secure, reliable integrations using Spring Boot, Spring WebFlux, PostgreSQL, Redis, JSON, XML and validation logic.}
  \item {Use Docker, Kubernetes, Git, GitHub Actions, Maven and CI/CD practices to support stable delivery and operational efficiency.}
  \item {Monitor and troubleshoot production systems using Grafana, Prometheus, NewRelic, logs and metrics to improve reliability.}
  \item {Improve quality through JUnit, Mockito, integration tests, API checks and maintainable service design.}
  \item {Collaborate in agile teams with product owners, QA, DevOps and engineers to turn complex requirements into working backend solutions.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring awareness and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\end{document}
