%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - Lead Solution Architect - Finance IT}, pdfauthor={Manisha Padhi}, pdfsubject={Lead Solution Architect - Finance IT}, pdfkeywords={Solution Architecture | Enterprise Integration | Finance IT Transformation}}

\name{Manisha}{Padhi}

\position{Solution Architecture | Enterprise Integration | Finance IT Transformation}

\address{Lgh 1301, Skoldvagen 7, Stockholm, 15151, Sweden}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Target Role}
\begin{cvskills}
  \cvskill{Company and role}{Scania - Lead Solution Architect - Finance IT}
  \cvskill{Location}{Sodertalje / Stockholm region, Sweden}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\cvsection{Professional Summary}
\begin{cvskills}
  \cvskill{Summary}{Senior software developer with 8+ years of experience in enterprise applications, backend services, integrations, databases, production systems and stakeholder collaboration.}
  \cvskill{Summary}{Relevant to Lead Solution Architect work through strong hands-on architecture foundations: APIs, microservices, data handling, secure interfaces, cloud/container awareness, integration design and maintainable enterprise solutions.}
  \cvskill{Summary}{Can support Finance IT transformation by bridging business and IT, documenting target-state decisions, aligning stakeholders and designing scalable, secure, value-driven solutions.}
\end{cvskills}

\cvsection{Target Role Fit}
\begin{cvitems}
  \item {Practical experience designing and maintaining APIs, microservices, database-backed systems, integrations and production-quality enterprise applications.}
  \item {Background in finance and economics plus software engineering supports understanding of Finance IT, legal/compliance-adjacent processes and ERP transformation contexts.}
  \item {Can collaborate with architects, product owners, DevOps, engineers and business stakeholders to align solution design with business goals.}
  \item {Relevant exposure to data platforms, APIs, event-driven architecture awareness, cloud concepts, AI/LLM interest and reusable data products.}
  \item {Strong communication, documentation, code review and mentoring habits that support architectural leadership and team guidance.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Architecture}{Solution design, API design, microservices, integration patterns, secure interfaces, scalability, maintainability, governance awareness}
  \cvskill{Enterprise IT}{Finance/economics background, ERP awareness, data platforms, legacy modernization, stakeholder alignment, capability mapping awareness}
  \cvskill{Technology}{Java 17/21, Spring Boot, REST APIs, PostgreSQL, SQL, Redis, Docker, Kubernetes, CI/CD, cloud concepts}
  \cvskill{Data and integration}{JSON, XML, data validation, query optimisation, event-driven architecture awareness, reusable data product interest}
  \cvskill{Leadership}{Code reviews, mentoring, technical documentation, cross-functional collaboration, business and IT communication}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Design, develop and maintain Java backend services, REST APIs and data integrations for business-critical production systems.}
  \item {Collaborate with product owners, QA, DevOps and engineers to align solution design with business needs, technical constraints and release goals.}
  \item {Use PostgreSQL, SQL, Redis, JSON and XML to support reliable data handling, validation, integration flows and service behaviour.}
  \item {Apply microservice, secure interface, CI/CD, Docker, Kubernetes and observability practices to improve scalability and maintainability.}
  \item {Review code, document workflows, mentor colleagues and share knowledge to support consistent engineering decisions and quality.}
  \item {Troubleshoot production issues using Grafana, Prometheus, NewRelic, logs and metrics, then feed learnings into technical improvements.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring awareness and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\end{document}
