%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - Vehicle Function Owner - Charging Domain}, pdfauthor={Manisha Padhi}, pdfsubject={Vehicle Function Owner - Charging Domain}, pdfkeywords={Vehicle Function Owner | Requirements | Backend Integration | Charging Domain}}

\name{Manisha}{Padhi}

\position{Vehicle Function Owner | Requirements | Backend Integration | Charging Domain}

\address{Lgh 1301, Skoldvagen 7, Stockholm, 15151, Sweden}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Target Role}
\begin{cvskills}
  \cvskill{Company and role}{Scania - Vehicle Function Owner - Charging Domain}
  \cvskill{Location}{Sodertalje / Stockholm region, Sweden}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\cvsection{Professional Summary}
\begin{cvskills}
  \cvskill{Summary}{Software Developer with 8+ years of IT experience connecting business needs, system behaviour, requirements, implementation, testing and production quality.}
  \cvskill{Summary}{Relevant to Scania/TRATON Vehicle Function Owner work through structured requirements handling, stakeholder communication, traceability mindset, integration testing, risk awareness and experience with complex distributed systems.}
  \cvskill{Summary}{Brings strong software engineering discipline for charging-related vehicle functions: translating needs into clear requirements, aligning teams and ensuring testable, reliable delivery.}
\end{cvskills}

\cvsection{Target Role Fit}
\begin{cvitems}
  \item {Can translate customer and stakeholder needs into clear functional requirements, acceptance criteria, test cases and delivery follow-up.}
  \item {Experienced managing dependencies across product owners, QA, DevOps, engineers and operational stakeholders in agile delivery.}
  \item {Strong testing and quality mindset through JUnit, Mockito, integration tests, API checks, production support and incident analysis.}
  \item {Relevant technical foundation in distributed systems, APIs, secure interfaces, data validation and reliable system behaviour.}
  \item {Motivated by electrification, charging systems, sustainable transport, functional safety and cyber security processes as learning domains.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Function ownership}{Requirements engineering, traceability, stakeholder input, dependency management, risk follow-up, test coverage, delivery readiness}
  \cvskill{System development}{Java, Spring Boot, REST APIs, microservices, distributed systems, secure interfaces, integration testing}
  \cvskill{Quality}{JUnit, Mockito, automated tests, API checks, validation, root-cause analysis, documentation}
  \cvskill{Domain alignment}{Battery electric vehicle interest, charging systems interest, functional safety awareness, cyber security awareness}
  \cvskill{Collaboration}{Product owners, architects, test engineers, QA, DevOps, agile teams, international communication}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Translate business and stakeholder needs into Java backend functionality, REST APIs, validation rules and testable service behaviour.}
  \item {Collaborate with product owners, QA, DevOps and engineers to clarify requirements, dependencies, risks and release readiness.}
  \item {Support traceability between requirements, implementation, integration tests, API checks and production monitoring evidence.}
  \item {Maintain reliable distributed services using PostgreSQL, SQL, Redis, JSON and XML with strong focus on data correctness and operational quality.}
  \item {Improve automated testing with JUnit, Mockito, integration tests and API checks to strengthen coverage and reduce delivery risk.}
  \item {Troubleshoot production issues using logs, metrics, Grafana, Prometheus and NewRelic, then document improvements and workflows.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring awareness and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\end{document}
