%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - Applied AI Solutions Engineer - TRATON R\&D AI Enablement}, pdfauthor={Manisha Padhi}, pdfsubject={Applied AI Solutions Engineer - TRATON R\&D AI Enablement}, pdfkeywords={Software Developer | Backend Services | APIs | Automation | AI-Enabled Workflows}}

\name{Manisha}{Padhi}

\position{Software Developer | Backend Services | APIs | Automation | AI-Enabled Workflows}

\address{Stockholm, Sweden | Female | EU long-term residence permit | No sponsorship required}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Professional Summary}
\vspace{-0.5ex}
\noindent\descriptionstyle{Software Developer with 8+ years of experience building backend services, APIs, automation and production systems, with practical exposure to AI-powered developer workflows and enterprise automation patterns.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Experienced translating unclear user and engineering needs into working prototypes, backend integrations, and production-ready services in collaboration with users, product owners, QA, DevOps, and engineering teams.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Brings a pragmatic build-first mindset for agentic workflows, including agentic architectures, tool use, guardrails, agent security, model tiering and hybrid deployments across frontier and smaller models.}\par

\cvsection{Selected Achievements and Highlights}
\begin{cvitems}
  \item {Analyzes business and engineering friction, separating deterministic logic, human review steps, agent/tool orchestration and AI-assisted workflow opportunities.}
  \item {Experienced building backend services, REST APIs, automation, testable integrations and CI/CD flows that can become reusable AI-enabled capabilities.}
  \item {Comfortable working hands-on with stakeholders to clarify ambiguous needs, prototype solutions and improve adoption based on feedback.}
  \item {8+ years of enterprise IT experience, including 3+ years focused on Java/Spring Boot backend development for production systems.}
  \item {Recognized career progression: promoted from Associate Trainee to Associate Consultant within 1 year.}
  \item {CMMI certified within 2 years and ranked top 3 in a Java certification course, supporting a quality-focused engineering profile.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{AI platforms}{LangChain, AutoCodeRover, Codex-style coding agents, ChatGPT Enterprise, Microsoft 365 Copilot, GitLab Duo, agentic workflows}
  \cvskill{Agentic architecture}{tool orchestration, human-in-the-loop design, guardrails, agent security, model tiering, GAIA-style evaluation, hybrid AI deployments}
  \cvskill{Developer tooling}{Git, GitHub Actions, CI/CD, Docker, Maven, test automation, documentation, repeatable delivery, developer enablement workflows}
  \cvskill{Model and data operations}{AWS CDK project exposure, PostgreSQL, SQL, Redis, JSON, XML, Hugging Face model consumption, Artifactory model repositories}
  \cvskill{Collaboration}{Technical discovery, stakeholder dialogue, mob/team collaboration mindset, fast feedback, knowledge sharing}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Build Java backend services and REST APIs that translate business needs into reliable, maintainable production functionality.}
  \item {Break down unclear requirements with product owners, QA, DevOps and engineers, then iterate toward working solutions with measurable delivery value.}
  \item {Use automated testing, integration checks, CI/CD and monitoring to improve speed, quality and confidence in software changes.}
  \item {Create documentation and share knowledge so teams can adopt repeatable workflows and operate services effectively.}
  \item {Explore AI-powered development tools and automation opportunities to improve engineering productivity and developer experience.}
  \item {Work with PostgreSQL, Redis, JSON, XML, Docker, Kubernetes, GitHub Actions, Grafana and logs to support practical integration and operational use cases.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
\end{cvskills}

\end{document}
