%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - Business IT Analyst - Technical Training and BCM}, pdfauthor={Manisha Padhi}, pdfsubject={Business IT Analyst - Technical Training and BCM}, pdfkeywords={Software Developer | Business IT Analysis | Agile Coordination | Training Support}}

\name{Manisha}{Padhi}

\position{Software Developer | Business IT Analysis | Agile Coordination | Training Support}

\address{Stockholm, Sweden | Female | EU long-term residence permit | No sponsorship required}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Professional Summary}
\vspace{-0.5ex}
\noindent\descriptionstyle{Software and business-oriented IT professional with 8+ years of experience across backend systems, stakeholder dialogue, agile delivery, documentation, training support and production operations.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Experienced in structured coordination, backlog follow-up, documentation quality, stakeholder communication, agile collaboration, and continuous improvement.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Combines technical understanding with clear communication to bridge business users, trainers, system owners and development teams in international environments.}\par

\cvsection{Selected Achievements and Highlights}
\begin{cvitems}
  \item {Coordinates backlog items, training activities, quality checks and stakeholder follow-up to create structure and clarity across business and IT teams.}
  \item {Experienced documenting workflows, supporting users, clarifying needs and communicating technical topics to non-technical stakeholders.}
  \item {Comfortable in agile teams with product owners, QA, DevOps, engineers and business stakeholders, including facilitation and follow-up.}
  \item {8+ years of enterprise IT experience, including 3+ years focused on Java/Spring Boot backend development for production systems.}
  \item {Recognized career progression: promoted from Associate Trainee to Associate Consultant within 1 year.}
  \item {CMMI certified within 2 years and ranked top 3 in a Java certification course, supporting a quality-focused engineering profile.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Business analysis}{stakeholder dialogue, requirements clarification, backlog coordination, process structure, activity follow-up, continuous improvement}
  \cvskill{Training and BCM}{training material quality checks, LMS coordination, user support, documentation ownership, knowledge sharing, learning setup improvement}
  \cvskill{Agile coordination}{Scrum/Kanban, agile ways of working, meeting facilitation, product owner collaboration, Jira-style coordination}
  \cvskill{Technical base}{Java, REST APIs, SQL, PostgreSQL, integrations, production systems, CI/CD, Grafana, troubleshooting}
  \cvskill{Communication}{International teams, business and IT bridge, clear English, Swedish-friendly workplace communication}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Work with product owners, QA, DevOps, engineers and stakeholders to clarify needs, coordinate delivery and follow up end-to-end changes.}
  \item {Document workflows, operational procedures and technical decisions to support knowledge sharing, onboarding and consistent delivery quality.}
  \item {Translate business needs into backend service behaviour, validation rules, API changes and testable acceptance criteria.}
  \item {Support production systems by analyzing incidents, communicating status, coordinating fixes and confirming release outcomes.}
  \item {Use agile delivery practices, CI/CD practices, automated testing and monitoring to improve transparency and team reliability.}
  \item {Collaborate with technical and non-technical colleagues in international environments using clear English and Swedish-friendly business communication.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
\end{cvskills}

\end{document}
