%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - Scrum Master - Security Platform, Software Update and Diagnostics}, pdfauthor={Manisha Padhi}, pdfsubject={Scrum Master - Security Platform, Software Update and Diagnostics}, pdfkeywords={Scrum Master | Agile Delivery | Java Backend | Diagnostics Platform}}

\name{Manisha}{Padhi}

\position{Scrum Master | Agile Delivery | Java Backend | Diagnostics Platform}

\address{Lgh 1301, Skoldvagen 7, Stockholm, 15151, Sweden}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Target Role}
\begin{cvskills}
  \cvskill{Company and role}{Scania - Scrum Master - Security Platform, Software Update and Diagnostics}
  \cvskill{Location}{Sodertalje / Stockholm region, Sweden}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\cvsection{Professional Summary}
\begin{cvskills}
  \cvskill{Summary}{Software Developer with 8+ years of IT experience and strong hands-on background in Java backend systems, agile delivery, production support and cross-functional collaboration.}
  \cvskill{Summary}{Well matched to Scania/TRATON Scrum Master work through experience with sprint-based delivery, product owners, QA, DevOps, engineers, code reviews, knowledge sharing, impediment handling, CI/CD and production-quality software.}
  \cvskill{Summary}{Brings practical technical credibility for teams working with backend services, microservices, diagnostics-adjacent platforms, connectivity, security mindset and continuous improvement.}
\end{cvskills}

\cvsection{Target Role Fit}
\begin{cvitems}
  \item {Can facilitate sprint planning, reviews, retrospectives and daily stand-ups from a developer perspective while keeping delivery focused on value, flow and quality.}
  \item {Experienced collaborating with product owners, QA, DevOps and engineers to align priorities, dependencies and release readiness in agile teams.}
  \item {Hands-on Java, Spring Boot, REST API, microservice, Kubernetes, CI/CD, Grafana and production support background gives credibility with technical teams.}
  \item {Comfortable coaching colleagues, reviewing code, documenting workflows and strengthening common ways of working across distributed teams.}
  \item {Motivated by TRATON values: customer first, respect, team spirit, responsibility and elimination of waste through continuous improvement.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Agile leadership}{Scrum ceremonies, sprint planning, reviews, retrospectives, daily stand-ups, backlog coordination, impediment removal, continuous improvement}
  \cvskill{Delivery}{Cross-functional teams, product owner collaboration, QA, DevOps, release readiness, documentation, stakeholder communication}
  \cvskill{Technical context}{Java 17, Spring Boot, REST APIs, microservices, PostgreSQL, Redis, Docker, Kubernetes, GitHub Actions, CI/CD}
  \cvskill{Observability}{Grafana, Prometheus, NewRelic, logging, metrics, incident analysis, production troubleshooting}
  \cvskill{Security platform fit}{Secure interfaces, API checks, integration testing, reliability, quality mindset, diagnostics and connectivity domain interest}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Develop and maintain Java 17 backend services for business-critical production systems using Spring Boot, REST APIs, microservices and databases.}
  \item {Work in cross-functional agile teams with product owners, QA, DevOps and engineers to deliver end-to-end changes with clear priorities and ownership.}
  \item {Support team flow by clarifying requirements, reviewing code, documenting workflows and helping colleagues resolve technical blockers.}
  \item {Improve delivery quality through JUnit, Mockito, integration tests, API checks, CI/CD practices and production monitoring.}
  \item {Use Kubernetes, Docker, Git, GitHub Actions, Maven, Grafana, Prometheus and NewRelic to support stable delivery and operational transparency.}
  \item {Coach colleagues, share knowledge and contribute to a developer chapter culture focused on learning, collaboration and continuous improvement.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring awareness and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
  \cvskill{Work authorization}{EU long-term residence permit; does not need sponsorship}
\end{cvskills}

\end{document}
