%!TEX TS-program = xelatex

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\hypersetup{pdftitle={Scania - DevOps Product Owner}, pdfauthor={Manisha Padhi}, pdfsubject={DevOps Product Owner}, pdfkeywords={Software Developer | DevOps | CI/CD | Developer Experience}}

\name{Manisha}{Padhi}

\position{Software Developer | DevOps | CI/CD | Developer Experience}

\address{Stockholm, Sweden | Female | EU long-term residence permit | No sponsorship required}

\mobile{+46 767852019}

\email{manishapadhi08@gmail.com}

\github{manishapadhi1}

\headersocialsep[ \textbar{} ]

\usepackage{import}

\begin{document}

\makecvheader

\cvsection{Professional Summary}
\vspace{-0.5ex}
\noindent\descriptionstyle{Senior software developer with 8+ years of IT experience across backend systems, CI/CD, containers, monitoring, production support and agile team collaboration.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Combines practical developer experience with backlog and priority collaboration, automation mindset, stakeholder communication, and focus on engineering productivity.}\par
\vspace{0.6ex}
\noindent\descriptionstyle{Can translate developer needs into clear platform value around CI/CD, infrastructure, automation, security, quality, observability and developer experience.}\par

\cvsection{Selected Achievements and Highlights}
\begin{cvitems}
  \item {Prioritizes DevOps capabilities that improve developer experience, CI/CD flow, quality gates, security, operational readiness and platform cost optimisation.}
  \item {Works with AWS, Kubernetes, Docker, GitLab/GitHub CI/CD pipelines, pipeline parallelisation, SonarQube-style quality gates and clean code practices.}
  \item {Collaborates with developers, architects, DevOps, QA, product owners and business stakeholders to translate technical platform needs into business value.}
  \item {8+ years of enterprise IT experience, including 3+ years focused on Java/Spring Boot backend development for production systems.}
  \item {Recognized career progression: promoted from Associate Trainee to Associate Consultant within 1 year.}
  \item {CMMI certified within 2 years and ranked top 3 in a Java certification course, supporting a quality-focused engineering profile.}
\end{cvitems}

\cvsection{Technical Skills}
\begin{cvskills}
  \cvskill{Product ownership}{DevOps backlog prioritization, roadmap input, stakeholder collaboration, business value translation, delivery capability follow-up}
  \cvskill{DevOps}{AWS, Kubernetes, Docker, GitLab CI/CD, GitHub Actions, pipeline parallelisation, Maven, Linux, OpenShift, automation}
  \cvskill{Platform engineering}{developer experience, engineering productivity, reusable workflows, clean code practices, SonarQube/code quality gates, secure delivery}
  \cvskill{Operations}{Grafana, Prometheus, NewRelic, logging, metrics, KPIs, troubleshooting, operationalisation, production support}
  \cvskill{Cost and tooling}{platform cost optimisation, Jira, Confluence, GitLab CI, Jenkins, AWS, Terraform, Ansible, Artifactory}
\end{cvskills}

\cvsection{Work Experience}
\begin{cventries}

\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{
\begin{cvitems}
  \item {Dockerize and maintain Java backend services and REST APIs, using Git, Maven, CI/CD practices and Kubernetes-based delivery patterns for stable releases.}
  \item {Improve delivery confidence through automated tests, integration checks, clean code practices and code review, with SonarQube-style quality gate alignment.}
  \item {Collaborate with product owners, QA, DevOps, architects and engineers to prioritize technical improvements, release readiness and operationalisation.}
  \item {Use Grafana, Prometheus, NewRelic, logs and metrics to monitor services, troubleshoot incidents and turn operational signals into reliability improvements.}
  \item {Contribute to developer experience through documentation, repeatable workflows, automation opportunities and reduced delivery friction across teams.}
  \item {Bring practical backend experience to DevOps product decisions around CI/CD pipeline design, pipeline parallelisation, platform cost optimisation, quality gates and secure delivery.}
\end{cvitems}
}

\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{
\begin{cvitems}
  \item {Built Java backend applications and ETL services for data-driven business processes.}
  \item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
  \item {Worked with SQL, relational databases, integration logic, automated tests and stakeholder clarification.}
\end{cvitems}
}

\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{
\begin{cvitems}
  \item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
  \item {Maintained business-critical systems, handled production incidents, analyzed root causes and communicated fixes.}
  \item {Improved batch jobs, data checks, reports and integration flows used by operations teams; promoted within 1 year.}
\end{cvitems}
}

\end{cventries}

\cvsection{Project Highlights}
\begin{cventries}

\cventry{Python, Docker, AWS CDK, CI/CD}{Smart Trader, Cloud Data Platform}{GitHub: manishapadhi1}{2024 to 2026}{
\begin{cvitems}
  \item {Built a backend and web application with service structure, tests and repeatable delivery.}
  \item {Used Docker, cloud infrastructure concepts and CI/CD practices to support maintainable operations.}
  \item {Practiced fintech-style data handling, automation, monitoring and reliable release flow.}
\end{cvitems}
}

\cventry{Elasticsearch, Fluentd, Kibana, Docker}{EFK Observability Stack}{GitHub: manishapadhi1}{2020}{
\begin{cvitems}
  \item {Worked with log aggregation using Elasticsearch, Fluentd and Kibana.}
  \item {Used Docker based environments to explore observability, monitoring and production visibility.}
\end{cvitems}
}

\cventry{Java, Docker, Keycloak, SSO}{Nexus SSO Integration}{GitHub: manishapadhi1}{2024}{
\begin{cvitems}
  \item {Studied and adapted a Java based single sign-on integration for secure backend access.}
  \item {Worked with Docker, Keycloak, authentication, access control and service configuration.}
\end{cvitems}
}

\end{cventries}

\cvsection{Education}
\begin{cventries}

\cventry{Masters in International Finance and Economics}{University of Macerata}{Macerata, Italy}{Sep 2019 -- Feb 2022}{
\begin{cvitems}
  \item {International Finance, Economics, Business Management}
\end{cvitems}
}

\cventry{Bachelor of Technology in Computer Science}{JNTU Kakinada}{Andhra Pradesh, India}{Sep 2013 -- May 2017}{
\begin{cvitems}
  \item {Computer Science, Java, Data Structures, DBMS, Software Engineering}
\end{cvitems}
}

\end{cventries}

\cvsection{Achievements and Certifications}
\begin{cvskills}
  \cvskill{Promotions}{Promoted from Associate Trainee to Associate Consultant within 1 year}
  \cvskill{Certifications}{CMMI Certified within 2 years. Ranked top 3 in Java Certification course}
  \cvskill{Languages}{Fluent in English; Swedish-friendly business communication context}
\end{cvskills}

\end{document}
