\newpage
\cvsection{Work Experience}
\begin{cventries}
\cventry{Senior Java Developer}{MSC Technology}{Torino, Italy}{Apr 2022 to Present}{\begin{cvitems}
\item {Develop new features and maintain current Java 17 backend code for business-critical production systems.}
\item {Build Spring Boot and Spring WebFlux services with REST APIs, secure interfaces and reliable integrations.}
\item {Work in cross functional agile teams with product owners, QA, DevOps and engineers to deliver end-to-end changes.}
\item {Use PostgreSQL, SQL, Redis, JSON and XML to support reliable data handling, validation and service behaviour.}
\item {Support microservices and distributed systems with clear ownership of well defined domains and service responsibilities.}
\item {Use Kubernetes, Docker, Git, GitHub, GitHub Actions awareness, Maven and CI/CD practices for stable delivery.}
\item {Monitor production systems with Grafana, Prometheus and NewRelic, and troubleshoot incidents using logs and metrics.}
\item {Improve automated testing with JUnit, Mockito, integration tests and API checks.}
\item {Take action on production issues, organize work, solve tasks and document workflows for operational efficiency.}
\item {Share knowledge, coach colleagues, review code and explore new technologies in a developer Chapter mindset where developers learn from others, share your knowledge and explore new technologies.}
\item {Communicate with Swedish and international colleagues in clear English and Swedish-friendly business contexts.}
\end{cvitems}}
\cventry{Associate Engineer - Backend}{Clariter}{Rome, Italy}{Aug 2021 to Feb 2022}{\begin{cvitems}
\item {Built Java backend applications and ETL services for data-driven business processes.}
\item {Developed REST APIs and secure authentication flows using JWT, OAuth2 and role-based access control.}
\item {Worked with SQL, relational databases, integration logic and automated tests for backend systems.}
\item {Used JUnit, API checks and data validation to improve maintainability and quality.}
\item {Collaborated with technical and non-technical stakeholders to clarify needs and deliver working solutions.}
\end{cvitems}}
\cventry{Associate Consultant}{Apps Associates}{Hyderabad, India}{Aug 2017 to Aug 2019}{\begin{cvitems}
\item {Developed and supported enterprise applications and integrations using Java, SQL and PL/SQL.}
\item {Maintained business-critical systems, handled production incidents and analysed root causes.}
\item {Improved batch jobs, data checks, reports and integration flows used by operations teams.}
\item {Worked directly with stakeholders to plan changes, explain issues and confirm releases.}
\item {Promoted from Associate Trainee to Associate Consultant within 1 year.}
\end{cvitems}}
\end{cventries}